---
title: "Essays in Microeconomics"
# subtitle: "The Effect of Racial and Ethnic Attitudes on Hispanic Identity in the U.S."
institution: "University of Houston"
author: "Hussain Hadah"
date: "4/13/2023"
header-includes:
   - \input{preamble}

output:
  beamer_presentation:
    slide_level: 3
    toc: true
    theme: "CambridgeUS"
    colortheme: "beaver"
    fonttheme: "structurebold"
    fig_width: 7
    fig_height: 5
    fig_caption: false
    #incremental: true
bibliography: AttitudesPaper.bib
biblio-style: apalike
#nocite: '@*'
---

```{r, include=FALSE}
options(tinytex.verbose = TRUE)
library(knitr)
knitr::opts_chunk$set(echo = FALSE)
```

```{r, include=FALSE}
options(tinytex.verbose = TRUE)
library(knitr)
knitr::opts_chunk$set(echo = FALSE)

### Load and install the packages that we'll be using today
if (!require("pacman")) install.packages("pacman")
pacman::p_load(tictoc, parallel, pbapply, future, future.apply, furrr, RhpcBLASctl, memoise, here, foreign, mfx, tidyverse, hrbrthemes, estimatr, ivreg, fixest, sandwich, lmtest, margins, vtable, broom, modelsummary, stargazer, fastDummies, recipes, dummy, gplots, haven, huxtable, kableExtra, gmodels, survey, gtsummary, data.table, tidyfast, dtplyr, microbenchmark, ggpubr, tibble, viridis, wesanderson, censReg, rstatix, srvyr, formatR, sysfonts, showtextdb, showtext, thematic, sampleSelection, RefManageR, DT, googleVis, png, gridExtra, grid, lattice, renderthis, chromote)
# devtools::install_github("thomasp85/patchwork")
remotes::install_github("mitchelloharawild/icons")
remotes::install_github("ROpenSci/bibtex")
remotes::install_github("jhelvy/renderthis", dependencies = TRUE)
remotes::install_github("rstudio/chromote")

# devtools::install_github("ajdamico/lodown")
### My preferred ggplot2 plotting theme (optional)
### https://github.com/hrbrmstr/hrbrthemes
# scale_fill_ipsum()
# scale_color_ipsum()
font_add_google("Fira Sans", "firasans")
font_add_google("Fira Code", "firasans")

showtext_auto()

theme_customs <- theme(
  text = element_text(family = 'firasans', size = 16),
  plot.title.position = 'plot',
  plot.title = element_text(
    face = 'bold', 
    colour = thematic::okabe_ito(8)[6],
    margin = margin(t = 2, r = 0, b = 7, l = 0, unit = "mm")
  ),
)

colors <-  thematic::okabe_ito(5)

# theme_set(theme_minimal() + theme_customs)
theme_set(hrbrthemes::theme_ipsum() + theme_customs)
### Set master directory where all sub-directories are located
mdir <- "~/Documents/GiT/Attitudes-and-Identity/presentations/jmp-presentation"

### Set working directories
pres_tabs <- paste0(mdir,"/tables")
pres_plots <- paste0(mdir,"/figures")

### Set working directory

# COLOR PALLETES
library(paletteer) 
# paletteer_d("awtools::a_palette")
# paletteer_d("suffrager::CarolMan")

### COLOR BLIND PALLETES
#paletteer_d("colorblindr::OkabeIto")
#paletteer_d("colorblindr::OkabeIto_black")
# paletteer_d("colorBlindness::paletteMartin")
# paletteer_d("colorBlindness::Blue2DarkRed18Steps")
# paletteer_d("colorBlindness::SteppedSequential5Steps")
# paletteer_d("colorBlindness::PairedColor12Steps")
# paletteer_d("colorBlindness::ModifiedSpectralScheme11Steps")
colorBlindness <- paletteer_d("colorBlindness::Blue2Orange12Steps")
cbbPalette <- c("#000000", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")

# scale_colour_paletteer_d("colorBlindness::ModifiedSpectralScheme11Steps", dynamic = FALSE)
# To use for fills, add
  scale_fill_manual(values="colorBlindness::Blue2Orange12Steps")

# To use for line and point colors, add
  scale_colour_manual(values="colorBlindness::Blue2Orange12Steps")
  #<a><button>[Click me](#sources)</button></a>
  
```

# Motivation

### The Role of Identity

-   Identity matters in many economic contexts [@akerlofEconomicsIdentity2000]

    -   A person's identity contributes to utility and affects decision-making [@akerlofEconomicsIdentity2000]

-   Identity could shift public opinions toward trade [@grossmanIdentityPoliticsTrade2021]

-   Racial and gender attitudes affect the racial and gender earnings gaps [@charlesPrejudiceWagesEmpirical2008; @charlesEffectsSexismAmerican2018]

-   Thus, it is important to understand if and how ethnic identities are chosen and shaped by society

\hyperlink{label}{\beamerbutton{I jump to the last slide}}


### Summary Statistics of CPS Sample

\input{tables/tab01-SumStat.tex}

\hypertarget{label}{\beamerbutton{I'm on the last slide}}


### References {.allowframebreaks}
